\documentclass[10pt,letterpaper]{article}

\usepackage[top=0.65in, bottom=0.65in, left=0.75in, right=0.75in]{geometry}
\usepackage{fontspec}
\setmainfont[
  BoldFont   = TeX Gyre Heros Bold,
  ItalicFont = TeX Gyre Heros Italic
]{TeX Gyre Heros}
\usepackage{microtype}
\usepackage{parskip}
\setlength{\parskip}{0pt}
\usepackage{enumitem}
\setlist[itemize]{leftmargin=1.2em, itemsep=3pt, parsep=0pt, topsep=3pt}
\usepackage{tabularx}
\usepackage{array}
\usepackage{hyperref}
\hypersetup{colorlinks=false, hidelinks}
\usepackage{fontawesome5}
\usepackage{titlesec}

\titleformat{\section}{\bfseries\small\scshape\uppercase}{}{0pt}{}
  [\vspace{2pt}\hrule\vspace{4pt}]
\titlespacing*{\section}{0pt}{10pt}{4pt}

\newcommand{\role}[3]{%
  \noindent\textbf{#1}\hfill{\small #2}\\
  {\small\textit{#3}}\par\vspace{3pt}%
}

% Boxed hyperlink — thin rule, tight padding
\newcommand{\lbox}[2]{%
  {\setlength{\fboxsep}{1.5pt}\fbox{\href{#1}{#2}}}%
}

\begin{document}
\pagestyle{empty}

% ── Header ───────────────────────────────────────────────────────────────────
\begin{center}
  {\fontsize{20pt}{24pt}\selectfont\bfseries DR.\ RISHI GURNANI}\\[5pt]
  {\small
    U.S.\ Citizen\quad|\quad
    \lbox{mailto:rishipgurnani@gmail.com}{rishipgurnani@gmail.com}\quad|\quad
    \lbox{https://rishigurnani.github.io}{rishigurnani.github.io}\quad|\quad
    \lbox{https://github.com/rishigurnani}{\faGithub\ rishigurnani}\quad|\quad
    $>$1,900 citations\quad
  }
\end{center}
{\rule{\linewidth}{1.2pt}}
\vspace{4pt}

% ── Summary ──────────────────────────────────────────────────────────────────
\section{Summary}

Principal-level Data Scientist and Software Engineer with a Ph.D.\ and 5$+$ years of
industry experience. Expert across the full data science lifecycle — data acquisition,
statistical modeling, deep learning architecture, and cloud-based production deployment —
with first-author papers published in \textit{Nature}. Four years as primary technical advisor and
solution architect for $>$20 enterprise clients. Keynote speaker; 16 publications; expert in deep learning.

% ── Core Competencies ────────────────────────────────────────────────────────
\section{Core Competencies}

\renewcommand{\arraystretch}{1.3}
\begin{tabularx}{\linewidth}{@{} >{\bfseries\small}p{0.21\linewidth} X @{}}
  Deep Learning   & Generative AI (VAE, GAN), GNNs, multitask learning, model ensembling, inference optimization \\
  Statistical     & Regression, classification, uncertainty quantification, feature engineering \\
  Cloud \& MLOps  & Cloud-based deployment and data pipelines, end-to-end ML lifecycle management \\
  Data Governance & Acquisition strategy, cleaning standards, scraping, compression \\
  Programming     & Python, PyTorch, PyTorch Geometric, NumPy, Scikit-learn, Pandas, FastAPI, HuggingFace, PyTest \\
\end{tabularx}

% ── Work Experience ───────────────────────────────────────────────────────────
\section{Work Experience}

\role{Senior Manager, Data Science for Global Ingredient Research — Coca-Cola}{Feb 2025 – present}{Atlanta, GA}
\begin{itemize}
  \item Leading three major end-to-end AI projects from data acquisition through cloud-based deployment:
    (1) multi-modal sensory prediction for beverage formulation, (2) personalized beverage recommendation systems,
    and (3) agentic generative ML for bioactive ingredient discovery.
\end{itemize}

\vspace{5pt}

\role{Director of Software Engineering \& Algorithms — Matmerize Inc.}{Mar 2021 – Feb 2025}{Atlanta, GA}
\vspace{3pt}
\begin{itemize}
  \item Sole developer of the deep learning core of our SaaS platform PolymRize$^{TM}$ ($\sim$100K lines of code, 5 languages)
    serving $>$1,000 users across $>$20 organizations.

  \item Managed a high-performing team of junior developers and interns, with alumni now in elite industry
    and academic roles, including \textbf{Meta}, \textbf{UC Berkeley (PhD)}, and \textbf{Georgia Tech (PhD)}.
\end{itemize}

% ── Education ─────────────────────────────────────────────────────────────────
\section{Education}

\begin{tabularx}{\linewidth}{@{} X r @{}}
  \textbf{Ph.D., Materials Science \& Engineering} — Georgia Tech (GPA 4.00) & 2019–2023 \\
  \multicolumn{2}{@{}l@{}}{\small\textit{Dissertation: Advances in AI for Accelerated Discovery of Energy Storage Polymers (GNNs \& Generative ML)}}\\[3pt]
  \textbf{M.S., Computer Science} — Georgia Tech (Specialization: Machine Learning) & \\[2pt]
  \textbf{B.S., Materials Science \& Engineering} — UC Berkeley & 2014–2018 \\
\end{tabularx}

% ── Awards & Talks ────────────────────────────────────────────────────────────
\section{Awards, Talks \& Open Source}

\begin{tabularx}{\linewidth}{@{} X r @{}}
  \textbf{Best Ph.D.\ Thesis}, Georgia Tech Sigma Xi        & 2024 \\
  \textbf{Graduate Student Award}, Materials Research Society & 2023 \\
  \textbf{Gold Medal, Best Presentation}, 2nd Energy \& Informatics International Forum & 2022 \\
\end{tabularx}

\vspace{5pt}

\noindent\textbf{Invited Talks:} Keynote, \lbox{https://www.riseconf.net/}{2024 RISE Conference};
Tokyo Institute of Technology (2022); Sandia National Laboratory (2021); nanoHUB ML Series (2021);
STLE 76th Annual Meeting (2022). Podcast: \lbox{https://www.youtube.com/watch?v=srLJlK67tXc}{\textit{It's a Material World}} (2023).

\vspace{5pt}

\noindent\textbf{Open Source:}
\lbox{https://github.com/rishigurnani/polygnn_trainer}{\faGithub\ \texttt{polygnn\_trainer}} —
PyTorch library for automated ML training, adopted by the materials informatics community.\quad
\lbox{https://github.com/rishigurnani/fintracker}{\faGithub\ \texttt{fintracker}} —
open-source personal finance analytics library.

% ── Publications ─────────────────────────────────────────────────────────────
\section{Publications \ {\normalfont\small(16 papers, $>$1,900 citations, h-index 15)}}

\begin{enumerate}[leftmargin=1.4em, itemsep=4pt, parsep=0pt, topsep=3pt]

  \item \lbox{https://www.nature.com/articles/s41467-024-50413-x}{AI-assisted discovery of high-temperature dielectrics for energy storage.}
    R Gurnani, S Shukla et al. \textit{Nature Communications} 15 (1), 2024. \textit{(93 citations)}

  \item \lbox{https://pubs.acs.org/doi/full/10.1021/acs.chemmater.2c02991}{Polymer informatics at scale with multitask graph neural networks.}
    R Gurnani, C Kuenneth, A Toland, R Ramprasad. \textit{Chemistry of Materials} 35 (4), 2023. \textit{(106 citations)}
  \item \lbox{https://rishigurnani.files.wordpress.com/2021/08/polyg2g-a-novel-machine-learning-algorithm-applied-to-the-generative-design-of-polymer-dielectrics.pdf}{PolyG2G: A novel machine learning algorithm applied to the generative design of polymer dielectrics.}
    R Gurnani, D Kamal, H Tran et al. \textit{Chemistry of Materials} 33 (17), 2021. \textit{(82 citations)}
  \item \lbox{https://www.nature.com/articles/s41578-024-00708-8}{Design of functional and sustainable polymers assisted by artificial intelligence.}
    H Tran, R Gurnani, C Kim et al. \textit{Nature Reviews Materials} 9 (12), 2024. \textit{(198 citations)}
  % 2025
  \item Stereoisomerism of Vicinal Polydichloronorbornene for Ultra-High-Temperature Capacitive Energy Storage.
    J Hao, S Shukla, R Gurnani et al. \textit{Advanced Materials} 37 (15), 2025.

  \item A physics-enforced neural network to predict polymer melt viscosity.
    A Jain, R Gurnani, A Rajan, HJ Qi, R Ramprasad. \textit{npj Computational Materials} 11 (1), 2025.

  \item Rationally designed high-temperature polymer dielectrics for capacitive energy storage: An experimental and computational alliance.
    PS Aklujkar, R Gurnani et al. \textit{Progress in Polymer Science} 161, 2025.

  \item Polymer composites informatics for flammability, thermal, mechanical and electrical property predictions.
    H Tran, C Kim, R Gurnani et al. \textit{Polymer Chemistry} 16 (30), 2025.

  % 2024

  \item Gas permeability, diffusivity, and solubility in polymers: Simulation-experiment data fusion and multi-task machine learning.
    BK Phan, KH Shen, R Gurnani et al. \textit{npj Computational Materials} 10 (1), 2024.

  \item Pendant group functionalization of cyclic olefin for high temperature and high-density energy storage.
    S Shukla, C Wu, A Mishra, R Gurnani et al. \textit{Advanced Materials} 36 (52), 2024.

  % 2023

  \item Effect of fluorine in redesigning energy-storage properties of high-temperature dielectric polymers.
    AA Deshmukh, C Wu, R Gurnani et al. \textit{ACS Applied Materials \& Interfaces} 15 (40), 2023.

  \item Identifying High-Performance Metal-Organic Frameworks for Low-Temperature Oxygen Recovery from Helium by Computational Screening.
    S Jamdade, R Gurnani, H Fang, SE Boulfelfel, R Ramprasad, DS Sholl. \textit{Industrial \& Engineering Chemistry Research} 62 (4), 2023.

  % 2021

  \item Interpretable machine learning-based predictions of methane uptake isotherms in metal-organic frameworks.
    R Gurnani, Z Yu, C Kim, DS Sholl, R Ramprasad. \textit{Chemistry of Materials} 33 (10), 2021.

  % 2020
  \item \lbox{https://rishigurnani.wordpress.com/wp-content/uploads/2020/11/5.0023759.pdf}{Machine-learning predictions of polymer properties with Polymer Genome.}
    H Doan Tran, C Kim, L Chen, R Gurnani et al. \textit{Journal of Applied Physics} 128 (17), 2020. \textit{(320 citations)}

  % 2018
  \item Experimental characterization of the shear properties of 3D-printed ABS and polycarbonate parts.
    S Rohde, J Cantrell, R Gurnani et al. \textit{Experimental Mechanics} 58 (6), 2018.

  % 2017
  \item Experimental characterization of the mechanical properties of 3D-printed ABS and polycarbonate parts.
    JT Cantrell, S Rohde, D Damiani, R Gurnani et al. \textit{Rapid Prototyping Journal} 23 (4), 2017. \textit{(777 citations)}

\end{enumerate}

\end{document}